---
title: "Program Kernel Density Estimation in `R`"
author: "Le Wang"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As we discussed in class, we can estimate the density function using following formula:

$$
\widehat{f}(x)=\frac{1}{N h} \sum \underbrace{\frac{1}{2} \cdot \mathbb{I}\left[\frac{X_{i}-x}{h} | \leq 1\right]}_{k\left(\frac{x_{i}-x_{i}}{h}\right)}
$$


This program illustrates how we can program in `R` this naive kernel density estimation approach with rectangular kernel and a pre-specified bandwidth. 

Let's generate some artificial Data for our analysis

```{r}
set.seed(123456)
X <- rnorm(10)
```

Specify the $x$ value that we would like to calculate the density for

$$
\widehat{f}(1)=\frac{1}{N h} \sum \underbrace{\frac{1}{2} \cdot \mathbb{I}\left[\mid \frac{X_{i}-1}{h} \mid \leq 1\right]}_{k\left(\frac{X_{i}-1} {h}\right)}
$$

```{r}
x <- 1
```

Let's also specify the bandwidht

```{r}
h <- 0.5
```


Then the formula becomes
$$
\widehat{f}(1)=\frac{1}{10 \times 0.5} \sum \underbrace{\frac{1}{2} \cdot \mathbb{I}\left[\mid \frac{X_{i}-1}{0.5} \mid \leq 1\right]}_{k\left(\frac{X_{i}-1} {0.5}\right)}
$$


# Calculate the distance between every data point and x
# and normalize the distance

```{r}
(X - x)/h
```

# Assign one to the data points falling in the interval

```{r}
k <- ifelse(abs((X-x)/h)<=1, 1, 0)
k
```


# Use the formulae to obtain kernel density estimate



```{r}
N <- length(X)
1/(N*h)*sum(1/2*k)
```


# This is optional. We will talk more about how to write a function later
# We can also write a function so that we can calculate this for many different values

```{r}
kpdf <- function(x, data, h){
  
  N <- length(data)
  k <- ifelse(abs((data-x)/h)<=1, 1, 0)
  
  return(1/(N*h)*sum(1/2*k))
  
}
```


```{r}
sapply(seq(-1,1,0.01), kpdf, data=X, h = h)
```



