---
title: "Hypothesis Testing: Various Examples"
output: html_notebook
---


## Test of Normality

Jarque-Bera (JB) Test of Normality

$$
  \frac{(\widehat{s}-0)^2}{6/N} + \frac{(\widehat{k}-3)^2}{24/N} \sim \chi^2_2
$$

Lets simulate some data to test whether or not our statistic works

```{r}
set.seed(123456)
x<-rnorm(1000)
x
```

Lets look calculate each component first
```{r}
library(moments)
s<-skewness(x)
k<-kurtosis(x)
s
k
```


Lets construct the test-statistic ourselves

```{r}
JBtest <- s^2/(6/1000) + (k-3)^2/(24/1000)

JBtest
```


Lets calculate the p-value

```{r}
1-pchisq(JBtest,df=2)
```

**Our interpretation:** There are 40.87048 percent of the values greater than the JB test statistic. Our test statistic is relatively small. Devitation is small, and we cannot reject the null hypothesis. 

Lets compare it to `R`'s built-in commmand:

```{r}
library(tseries)
jarque.bera.test(x)
```


# Test of Sample Mean

$$
\frac{(\overline{X}-\mu)}{\frac{\widehat{\sigma}}{\sqrt{N}}} \sim t_{N-1}
$$

Lets test whether or not it is equal to 0, which we know is true.

```{r}
t<-(mean(x)-0)/(sd(x)/sqrt(1000))
t
```

Lets compare it to a large value, be it negative or positive

```{r}
qt(.025, df=999)
qt(.975, df=999)
```

Let's calculate the p-value

```{r}
pt(-abs(t),df = 999)*2
```

Compare it to the built-in command in R

```{r}
t.test(x,mu=0)
```

Now lets test whether or not it is equal to 2, which we know is false

```{r}
t<-(mean(x)-2)/(sd(x)/sqrt(1000))
t
```


```{r}
qt(.025, df=999)
qt(.975, df=999)
```

```{r}
pt(-abs(t),df = 999)*2
```




## Test of Equal Variance

Lets simulate the data

```{r}
set.seed(123456)
x <- rnorm(50, mean = 0, sd = 1)
y <- rnorm(30, mean = 1, sd = 1)

```

Calculate the test statistic
```{r}
# Test Statistic
F<- var(x)/var(y)

```



Calculate p-value yourself
```{r}
1-pf(F,df1=49,df2 = 29)
```


**Conclusion:** p-value is much greater than 5 percent. It is not very extreme. We fail to reject the null hypothesis!

Lets' compare it to `R`'s built-in command for this purpose

```{r}
var.test(x, y, alternative = "greater")
```

