---
title: "Hypothesis Testing: Stock Analysis using R"
output: html_notebook
---


```{r}
library(quantmod)

# Obtain data
getSymbols(c('AAPL','GOOGL'), warnings = FALSE)

# Calculate returns
ret.AAPL <- diff(AAPL$AAPL.Adjusted)/lag(AAPL$AAPL.Adjusted)
ret.GOOGL <- diff(GOOGL$GOOGL.Adjusted)/lag(GOOGL$GOOGL.Adjusted)

# Omit missing observations
ret.AAPL <- na.omit(ret.AAPL)
ret.GOOGL <- na.omit(ret.GOOGL)

# Plot the time series
plot(ret.AAPL)
plot(ret.GOOGL)
```

## Does any of these stocks actually offer a real investment opportunity on average?

```{r}
mean(ret.AAPL)
```

```{r}
t<-
t
```


```{r}

```

Compare it to the built-in command in R

```{r}
t.test(ret.AAPL,mu=0)
```

## Do these two stocks have equal risks?

Test statistic:

$$
\frac{\widehat{\sigma}_x}{\widehat{\sigma}_y} \sim F_{N_1-1, N_2-1}
$$

1. Calculate the test statistic:

```{r}
var.x <- 
var.y <- 

# We will use the higher risk in the numerator
F<- 
F
```

2. Calculate the p-value

$$
\Pr[X \geq F]
$$

```{r}
# Lets calculate the degrees of freedom
N11 <- 
N21 <- 
N11
N21

# P-value

```


3. Lets verify our results using the built-in command

```{r}
var.test(ret.AAPL, ret.GOOGL, alternative = "greater")
```

4. What is your conclusion?

**Answer:**


## Is this stock normally distributed?

Jarque-Bera (JB) Test of Normality

$$
  \frac{(\widehat{s}-0)^2}{6/N} + \frac{(\widehat{k}-3)^2}{24/N} \sim \chi^2_2
$$


```{r}
library(moments)
s<-
k<-
s
k
```


Lets construct the test-statistic ourselves

```{r}
JBtest <- 

JBtest
```


Lets calculate the p-value

```{r}

```


```{r}
library(tseries)
jarque.bera.test(ret.AAPL)
```