---
title: "What is a large or unlikely number, Statistically speaking? and Quiz 10"
output: html_notebook
---


How do we know if 2 is a large value?

  1. **Large**, say, is defined as a value greater than **top 5 percent** (or $95^{th}$) of the distribution
  
# Positive Distributions

## Approach 1: Pre-specified large value
  
**Examples: Drawn from a $\chi^2_4$ distribution**

```{r}
qchisq(.95, 4)
```

**Exercise**

1. What if we change our definition of large to the top 50 percent of the distribution?
  
```{r}

```
  
2. What if we change our value from 2 to 10? And define the large as the top 1 percent of the distribution
  
```{r}

```

  
**Examples: Drawn from a $F_{1,15}$ distribution**

```{r}
qf(.95, 1, 15)
```


**Exercise**

1. What if we change our value from 2 to 5? And define the large as the top 1 percent of the distribution
  
```{r}

```


## Approach 2: Percentage of Larger values than the observed one.

**Examples: Drawn from a $\chi^2_4$ distribution**


```{r}
1-pchisq(2,4)
```

There are `r 1-pchisq(2,4)*100` percent of the values greater than 2. Not large! 


# General Distributions

## Standard Normal Distribution

### Approach 1

```{r}
qnorm(.975)
qnorm(.025)
```

### Approach 2
```{r}
pnorm(-2)*2
```

**Exercise**

1. What if we change our value from 2 to 5? And define the large as the top 1 percent of the distribution. 

```{r}

```

