---
title: "Tutorials on R and R Studio (Part V)"
author: "Le Wang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In class, you can download this set of code [here](intro-to-R_part5.R)

# Read Data

## Type 1: Text files

Data sometimes come with headers (the first row is variable names, not actual data!) You need to tell R that!
 
```{r}
  kids<-read.table("examples/Kids.txt",header=T)
```
  
Double click the kids data in the Session "Environment", you can have a spread-sheet type of view of the data. Let's call a variable in the data
  
```{r}
  kids$Bday
```
  

Remember that the `$` operator is one way to access an individual variable from within a data.frame object.

```{r}
attach(kids)
kids
```

  
## Type 2: CSV files
```{r}
  kids2<-read.csv("examples/Kids2.csv",header=T)
  attach(kids2)
  kids2
```

  
## Type 3: Delimited files  
```{r}
  kids3<-read.delim("examples/Kids3.prn",header=T)
  attach(kids3)
  kids3

```

  
  
## Type 4: Stata files

```{r}
  library(foreign)
  major <- read.dta("examples/major.dta")    
```
  
  
  
# Output Data

Create a matrix of data values. This 2 by 3 matrix is called "major"  

```{r}
  major<-matrix(c(632,576,435,520,623,397),nrow=2,byrow=T)
  major
```
  
Let's give names to these columns (treated as variables)

```{r}
  colnames(major)<-c("Sciences","Liberal Arts","Business")
# row names
  rownames(major)<-c("Male","Female")
# Let's look at the data again
  major  
```


Save the data in working directory in case you want to use this data again
```{r}
  write.table(major, file="examples/major.txt",row.names=FALSE)

```

Save To A Tab Delimited Text File
```{r}
  write.table(major, file="examples/major.txt",row.names=FALSE,sep="\t")

```

Or, Save to a Stata file and export data frame to Stata binary format 

```{r}
  library(foreign)
  write.dta(major, "examples/major.dta") 

# What to do?
  major<-data.frame(major)
  write.dta(major, "examples/major.dta")

```

# Quantmod package from Yahoo

```{r}
  # Install Quantmod package if you have not done so
  install.packages("quantmod")
  
  # Load the library
  library("quantmod")
  
  # Obtain the information on price and volume for Walmart
  getSymbols('WMT')

  # Take a look at the data (first six rows/dates)
  head(WMT)
  
  # Let's plot all the price data and add some indicators such as
  # volumes (addVo()) and Bollinger Bands (addBBands())
  chartSeries(WMT, subset='2010::2010-04', 
              theme = chartTheme('white'),
              TA="addVo();addBBands()")    
  
  # Use the built-in command to generate daily returns
  # We will explain in more detail why this is not necessarily
  # the best practice. 
  
  ret2 <- dailyReturn(WMT$WMT.Adjusted)
  # Examine the data
  View(ret2)
  
  # Suppose that we are only interested in a subset of the data
  # We will explain in detail why this should be employed in practice
  
  # Note that the date variable is not in my dataset, how to obtain
  # it? Use index()!
  
  WMT.2011<-subset(ret2,index(ret2) >="2011-01-01" & index(ret2) <="2011-12-31")
```


  
  
  
